### 2019-10-24 paper/paper.Rmd
working on app

## Extensions
ambiguity and disambiguation
Cross-situational extensions (Smith, Blythe) - most word learning situations are ambiguous and require disambiguation across time (using mechanisms of learning and memory)
Socio-pragmatic extensions - most word learning instances are disambiguated by social and pragmatic cues (and are unambiguous)
Experimental evidence from the “associations vs. hypotheses” debate

>>>>

## Extensions
ambiguity and disambiguation
Cross-situational extensions (Smith, Blythe) - most word learning situations are ambiguous and require disambiguation across time (using mechanisms of learning and memory)
Socio-pragmatic extensions - most word learning instances are disambiguated by social and pragmatic cues (and are unambiguous)
Experimental evidence from the "associations vs. hypotheses" debate
